\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-21 WOOT/Files/countermeasure.tex
[countermeasure] rm comment
exp,coutermeasure,util
Some comments about figures
minor revision of intro

\section{Countermeasures}
\yechang{Feng Liang says Andriod or iOS can provide an API to render private information only on onboard screen (like iPad OS)}

\label{sec:countermeasures}
Authorization mechanism like GoodUSB\cite{tian2015defending} has been proposed as a countermeasure against BadUSB attack. But as mentioned in Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on internal display to request for authorization, which can be hijacked by our \tool. Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but no defense at all for our \tool. Here we discuss some effective countermeasures against \tool.

@@

\textbf{Isolated UI Rendering}
During our experiment, we noticed that \tool is actually unable to redirect out the locking screen keyboard from the iPad OS. Instead, the keyboard is only available on the internal display. However, this defense is only enabled on the locking screen keyboard, other virtual keyboard is still vulnerable to our \tool. This mechanism has inspired us to propose a new defense against our \tool. If the OS provider like Apple/Google can implement a more generalized \emph{isolated UI rendering} that allows developer to decide whether a content is ``sensitive'' and where it should be rendered. To better illustrate this countermeasure idea, we drew the Figure~\ref{fig:isolated_ui}. In that figure, the password keyboard is set to be ``sensitive'' component while the other parts of the UI is not. Thus the renderer will only render the password keyboard on the trusted internal display and prevent untrusted external display like \tool to obtain sensitive data. We believe this is a promising way to defend users from attack like juice filming and our \tool.
\begin{figure}[htbp]
	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
	\caption{Isolated UI Rendering}
	\label{fig:isolated_ui}
\end{figure}

@@

>>>>

\section{Countermeasures}
\label{sec:countermeasures}
Authorization mechanism like GoodUSB\cite{tian2015defending} has been proposed as a countermeasure against BadUSB attack. But as mentioned in Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on internal display to request for authorization, which can be hijacked by our \tool. Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but no defense at all for our \tool. Here we discuss some effective countermeasures against \tool.

@@

@@

\textbf{Isolated UI Rendering}
During our experiment, we noticed that \tool is actually unable to redirect out the locking screen keyboard from the iPad OS. Instead, the keyboard is only available on the internal display. However, this defense is only enabled on the locking screen keyboard, other virtual keyboard is still vulnerable to our \tool. This mechanism has inspired us to propose a new defense against our \tool called \emph{Isolated UI Rendering}. As illustrated in Figure~\ref{fig:isolated_ui}, we designed two separated UI render driver, one is secure the other is insecure. When an application require to render, it can pass the content along with a tag identifying whether the content is ``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS will only pass it to the secure driver, which only trusts the internal display. On the other hand, if the content is tagged with ``insensitive'', then it will be passed to both secure and insecure driver, rendered on both internal and external display.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
	\caption{Isolated UI Rendering}\shuqing{Maybe we can increase the font?}
	\label{fig:isolated_ui}
\end{figure}

\begin{algorithm}[H]
	\SetAlgoLined
	\KwData{Application UI Content}
	\For{component C in content}{
		\eIf{C.tag is sensitive}{
			Send $C$ to secure driver
		}{
			Send $C$ to both drivers
		}
	}
	\caption{Isolated UI Render}
\end{algorithm}
